\begin{acknowledgements}
The past 6 years have been an exhilarating ride. Never in my (adult) life have I had the opportunity to absorb as much knowledge, learn so many things, and experience so many life changes and mental growth.
Besides the fantastic lectures on all sorts of topics one can attend at a university, the most important experiences have been the constant interactions with absolutely brilliant and kind-hearted people. First and foremost, I am forever thankful for the hundreds of hours I spent in the office of my advisor Frew, debating anything from language, databases, two-stroke engines, and rocket science. Considering that I came from quite a different educational background, I cannot even begin to express how thankful I am for all the patience and for all the things I learned (and for him forgiving me for all the things I refused to learn). Having to miss those weekly roundups after completing my degree certainly will leave a big hole in my life. Even though I, unfortunately, spent significantly less time with the rest of my committee members, Amr El Abbadi and Jeff Dozier, I am incredibly thankful for the unequivocally kind and helpful feedback and support they have provided.

I want to thank the good folks and my dear colleagues at Bayesics LLC, Kwo-Sen Kuo and Mike Rilee, Mike Bauer, and Dai-Hai Ton That, and at OPeNDAP, James Gallagher and Nathan Potter. The various projects we have worked together on over the past years have not only been a whole lot of fun but taught me so many invaluable things. I am incredibly thankful for their constant support and all of the knowledge they shared with me. Also, I want to thank Kuo and Mike, in particular, for giving me the opportunity to pursue a Ph.D. in triangles. Who would have figured?

Huge appreciation also goes Jeff Dozier, Ned Bair, and Timbo Stillinger for patiently explaining the beautiful colors of snow, providing ideas and feedback, and skiing with me. I particularly thank Jeff for (trying to) teach me that \emph{heat} is not a noun.

The constant help and support from the excellent staff at Bren and UCSB made my life worryless and allowed me to focus on my work without distractions. Without fail, Steve Miley, Kristine Duarte, Satie Airamé, Brad Hill, Mike Colee, and Aaron Martin promptly solved any problem I could possibly throw at them. I am grateful for the learning experience I had with my cohort, fellow Ph.D. students, and Professors at Bren, as well as the many students I had the chance to interact with. They sparked so many good ideas and helped me solidify my knowledge. Particularly, I would like to thank Gabriella Alberola, Prof. Mark Buntaine, Prof. Roland Geyer, and Patrick Hunnicutt for providing incredibly interesting use cases.

Possibly the most important group of people I want to thank for making my academic voyage over the last years absolutely unique are my friends and roommates. Spending endless hours debating science and life with Jason, Sam, Paul, Eva, Jonathan, Alan, Andre, Este, Will, Connor, Blaine, and my choosen family Jeff, Ishany, and Matthew has been not only a huge blast at any given time but also an incredible learning experience. Being surrounded by brilliant and kind people from all sorts of disciplines that are constantly driven to dissect facts, interpret data points, and establish and rebut theories and models is not only the best possible pastime but offered so much to learn.
To the same extent, my friends back home, Eric, Malte, Alex, Franzandra, and Johannes, have been nothing but supportive over the last years and the best foothold one could wish for. Finally, my parents; my dad Dieter for always having been curious; my mom Helga for always being there for me; my son Isach for making it all worthwhile.

I deeply appreciate the various funding I received from the \gls{NSF}, the \gls{NASA}, the \gls{ESIP}, and Bren throughout the past year. I appreciate the funding through \gls{NSF} \gls{IIS} grant 1302212\footnote{\url{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1302212}} and from the 2018 \gls{ESIP} lab, having allowed me to work on data citation, \gls{NASA} \gls{ACCESS} 17 program (Award number: 80NSSC18M0118)\footnote{\url{https://www.earthdata.nasa.gov/esds/competitive-programs/access/stare}} having allowed me to work on spatiotemporal indexing (and provided me with my adurious companion \texttt{schiss}), and the Bren fellowship having allowed me to focus on my research without any distractions.
\end{acknowledgements} 
